---
title: "cycleparking"
author: "Yuhei Ito"
date: "2020/10/7"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Change language settings.
Sys.setenv(LANG = "en")
Sys.setlocale("LC_ALL","English")

# Load necessary packages.
library(dplyr)
library(ggplot2)
library(tmap) # for static and interactive maps.
library(tmaptools)
library(sf) # for working with vector file.
library(RColorBrewer) # for choosing color.
```

## Read me
### input data
census.rda: Greater London's census data of 2011.
route.rda: route data obtained from PCT.
parking.rda: parking data merged from CID and OSM.
lsoa_msoa.rda: LSOA and MSOA link.

## Load data
```{r}
rm(list = ls()) # Clear R environment.
load(file="data/census.rda")    # Load census data.
load(file="data/route.rda")     # Load route data.
load(file="data/parking.rda")   # Load parking data.
load(file="data/area.rda")      # Load area data.
load(file="data/lsoa_msoa.rda") # Load lsoa_msoa data.
msoa = st_read("data/msoa.shp") # MSOA shape file.
```

## Join MSOA code to census
```{r}
# Join Origin MSOA
census = left_join(census, lsoa_msoa, by = c("olsoa" = "lsoa"))
any(is.na(census$msoa)) # False, join successful.
census$omsoa = census$msoa
census = census[,c("olsoa","omsoa","dlsoa","all","bicycle")]

# Join Destination MSOA
census = left_join(census, lsoa_msoa, by = c("dlsoa" = "lsoa"))
any(is.na(census$msoa)) # False, join successful.
census$dmsoa = census$msoa
census = census[,c("olsoa","omsoa","dlsoa","dmsoa","all","bicycle")]
```

## Join MSOA code to parking
```{r}
parking = left_join(parking, lsoa_msoa, by = c("lsoa" = "lsoa"))
any(is.na(parking$msoa)) # False, join successful.
parking = parking[,c("lsoa","msoa","space")]
```

## Aggregate census' all and bicycle by MSOA.
```{r}
census2 = 
  census %>%
  group_by(omsoa,dmsoa)%>%
  summarise(all = sum(all), bicycle = sum(bicycle))

sum(census2$all) == sum(census$all) #TRUE, successful.
```

## Add distance and hilliness to census2.
```{r}
# Delete rows with rf_dist_km and rf_avslope_perc are NA. These NA rows have Other or OD0000003 written on geo_code2 column.
route = 
  route %>%
  filter(!is.na(rf_dist_km))
any(is.na(route)) #FALSE, successful.

# CREATE JOIN ID.
# 1. Create join ID for Origin = geo_code1, Destination = geo_code2, ID = OD
route12 = route%>%as.data.frame()
route12$id = paste(route$geo_code1, route$geo_code2)
nrow(route12) #308782

# 2. Create join ID for Origin = geo_code2, Destination = geo_code1, ID = OD
route21 = route
route21$id = paste(route$geo_code2, route$geo_code1)
nrow(route21) #308782

# 3. Combine two dfs.
route = rbind(route12,route21)
nrow(route) #617564

# Remove duplication of ID which are intra-zonal OD pairs. Avoid adding duplicated rows when joining to census data.
route = 
  route %>% distinct(id, .keep_all = TRUE)

# Delete unnecessary column
route = route[,c("id", "rf_dist_km", "rf_avslope_perc")]
```

## Join distance and hilliness to census2.
```{r}
# Create join id for Census data.
census2$id = paste(census2$omsoa, census2$dmsoa)

# Join route data.
census2 = left_join(census2, route, by = "id")

# Delete id column
census2 = 
  census2 %>%
  select(-id)

```

## Check census data.
```{r}
any(is.na(census2)) #TRUE
  census2 %>%
  filter(is.na(rf_dist_km))
  
# Check if there is any No fixed place data on Census. -> No.
nrow(census2) #601902 rows.

census2 %>%
  mutate(First3D = substring(dmsoa,1,3)) %>% # Obtain first three letters of destination MSOA.
  filter(First3D == "E02") # Check if all rows are E02. 601902 rows Correct.

census2 %>%
  mutate(First3O = substring(omsoa,1,3)) %>% # Obtain first three letters of origin MSOA.
  group_by(First3O)%>%
  summarise(n(),sum(all),sum(bicycle)) # There are 4570 (bicycle n=97) commuters come from Wales.

# Identify intra-zonal trip.
census2$intra = ifelse(census2$omsoa == census2$dmsoa, TRUE, FALSE)
census2 %>%
  filter(intra == TRUE) %>%
  nrow() #983 rows

# Excluded rows?
census2$excluded = ifelse(is.na(census2$rf_dist_km), TRUE, FALSE)
```

## Check how many trips are excluded and how many are intra/inter zonal trips. (Table 6. Number of Commuters in/to Greater London) 
```{r}
# Total amount of travel to GL before excluding any trips.
sum(census2$all) # 3715982

# Intra and Inter zonal trips
census2 %>%
  group_by(intra) %>%
  summarise(n(),sum(all), sum(bicycle))

# Excluded and Included to the study.
census2 %>%
  group_by(excluded) %>%
  summarise(n(),sum(all), sum(bicycle))

# Intra/Inter and Exclude/Include.
census2 %>%
  group_by(excluded, intra) %>%
  summarise(n(),sum(all), sum(bicycle))

219452/nrow(census2)*100      # 36% OD pairs
570254/sum(census2$all)*100   # 15% all commuters
4017/sum(census2$bicycle)*100 # 3%  cycle commuters
```

# Government Target Equity 

## BCG construction Step 1: Eliminating >30km od and Calculate Government Target Equity (GE) propensity
```{r}
# Eliminate >30km OD pairs
census2 =
  census2 %>% #601902 od pairs
  filter(excluded == FALSE) %>% #382450 od pairs
  select(-c("excluded"))

# Calculate parameter for Government Target Equity (GE).
census2 =
  census2 %>%
  mutate(logit_ge = 
           -3.959 + 
           (-0.5963 * rf_dist_km) + 
           (1.866 * sqrt(rf_dist_km)) + 
           (0.008050 * rf_dist_km^2) +
           (-0.2710 * rf_avslope_perc) + 
           (0.009394 * rf_dist_km*rf_avslope_perc) + 
           (-0.05135 * sqrt(rf_dist_km) *rf_avslope_perc)
         )

# Calculate GE propensity.
census2$GEpct = exp(census2$logit_ge) / (1 + exp(census2$logit_ge))
```

## BCG construction Step 2: Calculate Government Target Equity (GE) number of cycle commuters for each OD pair.
```{r}
# Calculate future cycle commuter no. based on Government Target Equity (GE) scenario.
census2 =
  census2%>%
  mutate(bicycle_ge = bicycle + all*GEpct)

# Check
sum(census2$bicycle_ge)/sum(census2$bicycle) #1.6 times in total by GE scenario

# Rearrange columns
names(census2)

census2 = 
  census2[,c("omsoa","dmsoa","all","bicycle","bicycle_ge","GEpct","logit_ge","rf_dist_km","rf_avslope_perc","intra")]
```

## BCG construction Step 3: Aggregate by destination MSOA.
```{r}
# Aggregate based on destination MSOA.
census3 =
  census2 %>%
  group_by(dmsoa)%>%
  summarise(all = sum(all),
            bicycle = sum(bicycle),
            bicycle_ge = sum(bicycle_ge)
            )

# How many MSOAs in GL?
length(unique(census2$dmsoa)) #983

# Check
sum(census2$all) == sum(census3$all) # TRUE
sum(census2$bicycle) == sum(census3$bicycle) # TRUE
sum(census2$bicycle_ge) == sum(census3$bicycle_ge) # TRUE
```

## BCG construction Step 4: Construct BCG by mean values - Growth amount
```{r}
# Calculate current share for each MSOA
census3$CurrentShare = census3$bicycle/census3$all

# Calculate growth amount and add a new column.
census3$GrowthNosGE = census3$bicycle_ge - census3$bicycle

# Horizontal axis (Current AT share)
# If the share is lower than the mean, 1 otherwise 2.

BCG_x = ifelse(
  census3$CurrentShare < mean(census3$CurrentShare),
  1,2)

# Vertical axis (Growth AT share)
# If the share is lower than the mean, 1 otherwise 2.

BCG_y = ifelse(
  census3$GrowthNosGE < mean(census3$GrowthNosGE),
  1,2)

# Combine the above two.
BCG = paste(BCG_x,BCG_y,sep="")

# Rename the codes to BCG terms.
BCG = recode(BCG, 
              '11' = "Problematic", 
              '12' = "Promising",
              '21' = "Achieved",
              '22' = "Maturing")

# Add a column.
census3$BCGNosGE = BCG

census3$BCGNosGE = factor(census3$BCGNosGE, 
                levels = c("Achieved","Maturing","Promising","Problematic"))

census3%>%
  select(GrowthNosGE,BCGNosGE)%>%
  filter(census3$GrowthNosGE > mean(census3$GrowthNosGE))%>%
  group_by(BCGNosGE)%>%
  summarise(n())
```

## Parking 1: Aggregate parking space for each MSOA
```{r}
# the updated parking data
sum(parking$space) #140788

# Aggregate parking capacity based on MSOA
parking2 =
  parking %>%
  select(msoa, space) %>%
  group_by(msoa) %>%
  summarise(space = sum(space))

sum(parking2$space) == sum(parking$space) #140788 TRUE
```

## Parking 2: Join parking space to census
```{r}
census3 = left_join(census3, parking2, by = c("dmsoa" = "msoa"))
sum(census3$space) == sum(parking2$space) #TRUE Successful!
```

# Parking Occupancy Rate: por

4 Categories:
Surplus  : Less than 50% occupancy rate
Ideal    : 50% and more and 80% and less occupancy rate
Threshold: More than 80% and 100% and less occupancy rate
Shortage : More than 100% occupancy rate

Examples:
Surplus  : bicycle= 30, parking=100 - Less than 50% occupancy rate
Ideal    : bicycle= 70, parking=100 - 50% and more and 80% and less occupancy rate
Threshold: bicycle= 90, parking=100 - More than 80% and 100% and less occupancy rate
Shortage : bicycle=110, parking=100 - More than 100% occupancy rate

Exceptions:
Case 1   : bicycle= 0, parking=100 -> Surplus  (n = 22 current)
Case 2   : bicycle=10, parking=0   -> Shortage (n = 1  current)
Case 3   : bicycle= 0, parking=0   -> Shortage (n = 0  observation)

## Current Occupancy Rate and Category
```{r}
# Current Occupancy Rate
census3$porCurrent = census3$bicycle / census3$space

census3%>%
  filter(bicycle == 0)
census3%>%
  filter(space == 0)

# Categorise into 4.
## 2011 Occupancy Rate
census3 = 
  census3 %>%
    mutate(porCurrentCat = ifelse(porCurrent > 1, "Shortage", 
                          ifelse(0.8 < porCurrent & porCurrent <= 1, "Threshold",
                                 ifelse(0.5 <= porCurrent & porCurrent <= 0.8, "Ideal",
                                        ifelse(0.5 > porCurrent, "Surplus",NA))))
           )
census3
```

## Future Occupancy Rate and Category
```{r}
# Future Occupancy Rate GE
census3$porFutureGE = census3$bicycle_ge / census3$space

# Categorise into 4.
## Occupancy Rate GE
census3 = 
  census3 %>%
    mutate(porFutureGECat = ifelse(porFutureGE > 1, "Shortage", 
                          ifelse(0.8 < porFutureGE & porFutureGE <= 1, "Threshold",
                                 ifelse(0.5 <= porFutureGE & porFutureGE <= 0.8, "Ideal",
                                        ifelse(0.5 > porFutureGE, "Surplus",NA))))
           )

census3
```

## Reorder factor of por categorisation
```{r}
# Convert to factor.
census3$porCurrentCat = as.factor(census3$porCurrentCat)
census3$porFutureGECat = as.factor(census3$porFutureGECat)

# Check levels
levels(census3$porCurrentCat)
levels(census3$porFutureGECat)
#"Ideal"     "Shortage"  "Surplus"   "Threshold"

# Reorder factor levels
census3$porCurrentCat = factor(census3$porCurrentCat, 
                levels = c("Surplus","Ideal","Threshold","Shortage"))
census3$porFutureGECat = factor(census3$porFutureGECat, 
                levels = c("Surplus","Ideal","Threshold","Shortage"))

# Check levels
levels(census3$porCurrentCat)
levels(census3$porFutureGECat)
#"Surplus"   "Ideal"     "Threshold" "Shortage" 
```

## Join census 3 dataframe to shapefile msoa
```{r}
msoa = left_join(msoa,census3, by = c("msoa" = "dmsoa"))
```

# Color setting
Reference:
https://www.datanovia.com/en/blog/the-a-z-of-rcolorbrewer-palette/
```{r}
display.brewer.pal(n = 11, name = "RdYlBu") 
brewer.pal(n = 11, name = "RdYlBu") 

BCGcol = c( "#73d87d", "#368cd3", "#FEC44F", "#ff3b40")
col_pocu = c("#4575B4", "#74ADD1", "#FEE090", "#D73027")
barplot(c(5,5,5,5), col=col_pocu) # Check
barplot(c(5,5,5,5), col=BCGcol) # Check
```

# Figures

### Map of current and growth nos of cyclist
```{r}
# current cyclists
gp=
  tm_shape(msoa) +
  tm_polygons(col = "bicycle",
              style = "fixed",
              breaks = c(0,10,10^2,10^3,10^4,21982),
              palette = brewer.pal(n = 5, name = "YlOrRd"),
              title = "Current Number of Cycle Commuters' Arrival",
                    )+
  tm_layout(legend.title.size = 0.9,
            legend.text.size = 0.7,
            legend.outside = TRUE,
            legend.outside.position = "bottom",
            ) 

tmap_save(gp, file="output/fig2a_CurrentNoCyclists.png", dpi =600, width=3, height=3.5)

# growth cyclists
gp=
  tm_shape(msoa) +
  tm_polygons(col = "GrowthNosGE",
              style = "fixed",
              breaks = c(0,10,10^2,10^3,10^4,21982),
              palette = brewer.pal(n = 5, name = "YlOrRd"),
              title = "Growth Number of Cycle Commuters' Arrival",
                    )+
  tm_layout(legend.title.size = 0.9,
            legend.text.size = 0.7,
            legend.outside = TRUE,
            legend.outside.position = "bottom",
            ) 

tmap_save(gp, file="output/fig2b_IncreaseNoCyclists.png", dpi =600, width=3, height=3.5)

sum(msoa$all) #3145728
sum(msoa$bicycle) #143182
sum(msoa$bicycle)/sum(msoa$all)*100 #4.551633
19.5168/4.551633
```

### Map of current share of cyclist
```{r}
# Select colors from a palette.
display.brewer.all(colorblindFriendly = TRUE) # display all colorblind-friendly colors


msoa$CurrentSharePct = msoa$CurrentShare*100 #Create new column

gp= 
  tm_shape(msoa) +
  tm_polygons(col = c("CurrentSharePct"),
              style = "fixed",
              breaks = c(0,2,4,6,9,15),
              palette = brewer.pal(n = 5, name = "PuBu"),
              title = c("Current Share of Cycle Commuter"),
              legend.format=list(fun=function(x) paste0(formatC(x, digits=0, format="f"), "%"))
              )+
  tm_layout(legend.title.size = 0.9,
            legend.text.size = 0.7,
            legend.outside = TRUE,
            legend.outside.position = "bottom",
            ) 

tmap_save(gp, file="output/fig2c_PctCyclists.png", dpi =600, width=3, height=3.5)

msoa = msoa[-c(which(colnames(msoa)=="CurrentSharePct" ))] # Delete created column 

```

### Spatial Distribution of Cycle Parking Supply
```{r}
gp= 
  tm_shape(msoa) +
  tm_polygons(col = "space",
              style = "fixed",
              breaks = c(0, 100, 300, 600, 1000, 1500, 3010),
              palette = brewer.pal(n = 5, name = "BuGn"),
              title = "Parking Supply")+
  tm_layout(legend.title.size = 0.9,
            legend.text.size = 0.7,
            legend.outside = TRUE,
            legend.outside.position = "bottom",
            ) 

tmap_save(gp, file="output/fig2d_ParkingSupply.png", dpi =600, width=3, height=3.5)
```

### Scatter Plot of Growth and Current Share of Cycle Commuter - Growth Amount Vesion Log scale
```{r,fig.width = 10, fig.asp = 1}
mean(census3$CurrentShare) #0.03563695
mean(census3$GrowthNosGE) #101.5944

test = ggplot(census3, aes(x = CurrentShare, y = GrowthNosGE)) +
  geom_point(aes(color = BCGNosGE), size = 1.2, show.legend = FALSE) +
  scale_colour_manual(values=BCGcol) + 
  labs(colour = "Mode Share Matrix Quadrants")+
  labs(y="Growth Amount of Cycle Commuter", x = "Current Commuter Cycling Mode Share")+
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

gp=
  test + scale_y_continuous(trans = 'log10')+ 
  geom_line(aes(x = mean(CurrentShare))) +
  geom_line(aes(y = mean(GrowthNosGE))) +
  geom_text(aes(x = 0.13, y = 115, label = "Mean value = 102", family = "sans")) +
  geom_text(aes(x = 0.035, y = 7500, label = "Mean value = 3.5%", family = "sans")) +
  geom_text(aes(x = 0.06, y = 30, label = "Achieved", family = "sans")) +
  geom_text(aes(x = 0.06, y = 400, label = "Maturing", family = "sans")) +
  geom_text(aes(x = 0.01, y = 400, label = "Promising", family = "sans")) +
  geom_text(aes(x = 0.01, y = 30, label = "Problematic", family = "sans")) 

ggsave(file="output/fig3_ScatterPlot.png", plot=gp, dpi =600, width=7, height=7)
```

### Spatial Distribution of BCG Categories
```{r}
gp=
  tm_shape(msoa) +
  tm_polygons(col = "BCGNosGE", palette = BCGcol,
              title = "Mode Share\nMatrix Quadrants")+
  tm_layout(legend.title.size = 1,
            legend.text.size = 0.75,
            legend.position = c("right","bottom"),
            ) 

tmap_save(gp, file="output/fig4_ModeShareMatrix.png", dpi =600, width=6, height=5)

```

### Spatial Distribution of Cycle Parking Supply
```{r}
tm_shape(msoa) +
  tm_polygons(col = "space",
              style = "fixed",
              breaks = c(0, 100, 300, 600, 1000, 1500, 3010),
              palette = brewer.pal(n = 5, name = "BuGn"),
              title = "Parking Supply")+
  tm_layout(legend.title.size = 1,
            legend.text.size = 0.75,
            legend.position = c("right","bottom"),
            ) 
```

### Stats for Parking Supply
```{r}
sum(msoa$bicycle) #143182

# Obtain area of each MSOA
msoa$area = st_area(msoa)

# TOP MSOAS
# Select MSOAs with more than 1000 cycle parkings
msoa %>%
  as.data.frame()%>%
  select(msoa, space)%>%
  arrange(desc(space))%>%
  filter(space>1000)%>% 
  nrow()#13
# These are 13 MSOAs

msoa %>%
  as.data.frame()%>%
  select(msoa, space,area)%>%
  arrange(desc(space))%>%
  filter(space>1000)%>%
  select(space)%>%
  sum()/sum(msoa$space)*100 #13.9742 
# Total of cycle parking at these MSOAs account for 14% of all cycle parkings in Greater London.

msoa %>%
  as.data.frame()%>%
  select(msoa, space,area)%>%
  arrange(desc(space))%>%
  filter(space>1000)%>%
  select(area)%>%
  sum()/sum(msoa$area)*100 #1.472863  
# Total of area of these MSOAs account for 1% of Greater London area.

# BOTTOM MSOAS
# Select MSOAs with less than 100 cycle parkings
msoa %>%
  as.data.frame()%>%
  select(msoa, space)%>%
  arrange(desc(space))%>%
  filter(space<100)%>% 
  nrow()#579
# These are 579 MSOAs

msoa %>%
  as.data.frame()%>%
  select(msoa, space,area)%>%
  arrange(desc(space))%>%
  filter(space<100)%>%
  select(space)%>%
  sum()/sum(msoa$space)*100 #17.61514 
# Total of cycle parking at these MSOAs account for 14% of all cycle parkings in Greater London.

msoa %>% 
  as.data.frame()%>%
  select(msoa, space,area)%>%
  arrange(desc(space))%>%
  filter(space<100)%>%
  select(area)%>%
  sum()/sum(msoa$area)*100 #67.19098   
# Total of area of these MSOAs account for 67% of Greater London area.

msoa = msoa[-c(which(colnames(msoa)=="area" ))] # Delete created column 
```

### Spatial Distribution of Parking Occupancy Category for Current Scenario
```{r}
tm_shape(msoa) +
  tm_polygons(col = "porCurrentCat", 
              palette = col_pocu,
              title = "Current\nParking\nOccupancy")+
  tm_layout(legend.title.size = 1,
            legend.text.size = 0.75,
            legend.position = c("right","bottom"),
            ) 

tm_shape(msoa) +
  tm_polygons(col = "porFutureGECat", 
              palette = col_pocu,
              title = "Future\nGovernment\nTarget (Equity)\nParking\nOccupancy")+
  tm_layout(legend.title.size = 1,
            legend.text.size = 0.75,
            legend.position = c("right","bottom"),
            ) 
```

### Number of cyclists destined to each category of parking occupancy
```{r,fig.width = 5, fig.asp = 0.7}
ggplot(census3,aes(fill=porCurrentCat, x = porCurrentCat, y = bicycle)) +
  geom_bar( stat="identity")+
  scale_fill_manual(values=col_pocu)+
  labs(y="No. of Commuter by Bicycle", x = "Parking Occupancy Category")

# Statistics of the number of cyclists destined to each occupancy rate category
census3 %>%
  group_by(porCurrentCat)%>%
  summarise(bicycle = sum(bicycle))%>%
  mutate(pct = bicycle/sum(bicycle)*100)

census3 %>%
  filter(space > 0)%>%
  select(porCurrent, bicycle, space,porCurrentCat)%>%
  summarise(mean= mean(porCurrent), sd=sd(porCurrent))
```

### Breakdown of Parking Occupancy Category based on No. of Cyclist for Current Scenario and Future Scenario
```{r,fig.width = 5, fig.asp = 0.7}
# Current scenario
tbd =
  census3 %>%
  group_by(BCGNosGE, porCurrentCat) %>%
    summarise(count = n(), cyclists = sum(bicycle))

# Count Stacked barchart
ggplot(tbd, aes(fill=porCurrentCat, y=cyclists, x=BCGNosGE))  + 
    geom_bar(position="stack", stat="identity")+
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of Cyclist", x = "Mode Share Matrix Quadrants")

# Percent stacked barchart
ggplot(tbd, aes(fill=porCurrentCat, y=cyclists, x=BCGNosGE))  + 
    geom_bar(position="fill",  stat="identity", ) +
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of Cyclist", x = "Mode Share Matrix Quadrants")

# Stats - No. of cyclists destined to each mode share matrix.
census3 %>%
  group_by(BCGNosGE)%>%
  summarise(bicycle = sum(bicycle))%>%
  mutate(pct = bicycle/sum(bicycle)*100)

# Stats - BCG x POR
tbd %>%
  group_by(BCGNosGE)%>%
  mutate(pct = cyclists/sum(cyclists)*100)

```

### Percentage Breakdown of Parking Occupancy Category based on No. of Cyclist for Current Scenario and Future Scenario 
```{r,fig.width = 5, fig.asp = 0.7}
# Future scenario
# Group by BCG and parking availability category based on GE
tbd =
  census3 %>%
  group_by(BCGNosGE, porFutureGECat) %>%
    summarise(count = n(), cyclists = sum(bicycle_ge))

# Count Stacked barchart
ggplot(tbd, aes(fill=porFutureGECat, y=cyclists, x=BCGNosGE))  + 
    geom_bar(position="stack", stat="identity")+
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of Cyclist", x = "Mode Share Matrix Quadrants")

# Percent stacked barchart
ggplot(tbd, aes(fill=porFutureGECat, y=cyclists, x=BCGNosGE))  + 
    geom_bar(position="fill",  stat="identity", ) +
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of Cyclist", x = "Mode Share Matrix Quadrants")

```
