---
title: "cycleparking"
author: "Yuhei Ito"
date: "2020/10/7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Change language settings.
Sys.setenv(LANG = "en")
Sys.setlocale("LC_ALL","English")

# Load necessary packages.
library(dplyr)
library(ggplot2)
library(e1071) #for calculating skewness.
```

## Read me
### input data
census.rda: A census data of 2011 subsetting by Greater London.
route.rda: route data obtained from PCT.
parking.rda: parking data merged from CID and OSM.
lsoa_msoa.rda: LSOA and MSOA link.

## Load data
```{r}
# Load census data.
census = paste(getwd(),"/data/census.rda", sep = "")
load(census)

# Load route data.
route = paste(getwd(),"/data/route.rda", sep = "")
load(route)

# Load parking data.
parking = paste(getwd(),"/data/parking.rda", sep = "")
load(parking)

# Load area data.
area = paste(getwd(),"/data/area.rda", sep = "")
load(area)

# Load lsoa_msoa data.
lsoa_msoa = paste(getwd(),"/data/lsoa_msoa.rda", sep = "")
load(lsoa_msoa)
```

## Join MSOA code to census
```{r}
# Join Origin MSOA
census = left_join(census, lsoa_msoa, by = c("olsoa" = "lsoa"))
any(is.na(census$msoa)) # False, join successful.
census$omsoa = census$msoa
census = census[,c("olsoa","omsoa","dlsoa","all","bicycle")]

# Join Destination MSOA
census = left_join(census, lsoa_msoa, by = c("dlsoa" = "lsoa"))
any(is.na(census$msoa)) # False, join successful.
census$dmsoa = census$msoa
census = census[,c("olsoa","omsoa","dlsoa","dmsoa","all","bicycle")]
```

## Join MSOA code to parking
```{r}
parking = left_join(parking, lsoa_msoa, by = c("lsoa" = "lsoa"))
any(is.na(parking$msoa)) # False, join successful.
parking = parking[,c("lsoa","msoa","space")]
```

## Aggregate census' all and bicycle by MSOA.
```{r}
census2 = 
  census %>%
  group_by(omsoa,dmsoa)%>%
  summarise(all = sum(all), bicycle = sum(bicycle))

sum(census2$all) == sum(census$all) #TRUE, successful.
```

## Add distance and hilliness to census2.
```{r}
# Delete rows with rf_dist_km and rf_avslope_perc are NA. These NA rows have Other or OD0000003 written on geo_code2 column.
route = 
  route %>%
  filter(!is.na(rf_dist_km))
any(is.na(route)) #FALSE, successful.

# CREATE JOIN ID.
# 1. Create join ID for Origin = geo_code1, Destination = geo_code2, ID = OD
route12 = route
route12$id = paste(route$geo_code1, route$geo_code2)
nrow(route12) #308782

# 2. Create join ID for Origin = geo_code2, Destination = geo_code1, ID = OD
route21 = route
route21$id = paste(route$geo_code2, route$geo_code1)
nrow(route21) #308782

# 3. Combine two dfs.
route = rbind(route12,route21)
nrow(route) #617564

# Remove duplication of ID which are intra-zonal OD pairs. Avoid adding duplicated rows when joining to census data.
route = 
  route %>% distinct(id, .keep_all = TRUE)

# Delete unnecessary column
route = route[,c("id", "rf_dist_km", "rf_avslope_perc")]
```

## Join distance and hilliness to census2.
```{r}
# Create join id for Census data.
census2$id = paste(census2$omsoa, census2$dmsoa)

# Join route data.
census2 = left_join(census2, route, by = "id")

# Delete id column
census2 = 
  census2 %>%
  select(-id)

any(is.na(census2)) #TRUE
  census2 %>%
  filter(is.na(rf_dist_km))
```

## Check census data.
```{r}
# Check if there is any No fixed place data on Census. -> No.
nrow(census2) #601902 rows.

census2 %>%
  mutate(First3D = substring(dmsoa,1,3)) %>% # Obtain first three letters of destination MSOA.
  filter(First3D == "E02") # Check if all rows are E02. 601902 rows Correct.

census2 %>%
  mutate(First3O = substring(omsoa,1,3)) %>% # Obtain first three letters of origin MSOA.
  group_by(First3O)%>%
  summarise(n(),sum(all),sum(bicycle)) # There are 4570 (bicycle n=97) commuters come from Wales.

# Identify intra-zonal trip.
census2$intra = ifelse(census2$omsoa == census2$dmsoa, TRUE, FALSE)
census2 %>%
  filter(intra == TRUE) %>%
  nrow() #983 rows

# Excluded rows?
census2$excluded = ifelse(is.na(census2$rf_dist_km), TRUE, FALSE)
```

## Check how many trips are excluded and how many are intra/inter zonal trips. (Table 6. Number of Commuters in/to Greater London) 
```{r}
knitr::opts_chunk$set(eval = FALSE)

# Total amount of travel to GL before excluding any trips.
sum(census2$all) # 3715982

# Intra and Inter zonal trips
census2 %>%
  group_by(intra) %>%
  summarise(n(),sum(all), sum(bicycle))

# Excluded and Included to the study.
census2 %>%
  group_by(excluded) %>%
  summarise(n(),sum(all), sum(bicycle))

# Intra/Inter and Exclude/Include.
census2 %>%
  group_by(excluded, intra) %>%
  summarise(n(),sum(all), sum(bicycle))

219452/nrow(census2)*100      # 36% OD pairs
570254/sum(census2$all)*100   # 15% all commuters
4017/sum(census2$bicycle)*100 # 3%  cycle commuters
```

## BCG construction Step 1: Eliminating >30km od and CalculateGoDutch propensity
```{r}
# Eliminate >30km OD pairs
census2 =
  census2 %>% #601902 od pairs
  filter(excluded == FALSE) %>% #382450 od pairs
  select(-c("excluded"))

# Calculate parameter for Go Dutch.
census2 =
  census2 %>%
  mutate(logit_gd = 
           -3.959 + 
           (-0.5963 * rf_dist_km) + 
           (1.866 * sqrt(rf_dist_km)) + 
           (0.008050 * rf_dist_km^2) +
           (-0.2710 * rf_avslope_perc) + 
           (0.009394 * rf_dist_km*rf_avslope_perc) + 
           (-0.05135 * sqrt(rf_dist_km) *rf_avslope_perc) +
           2.523 +
           (-0.07626*rf_dist_km)
         ) 

# Calculate GD propensity.
census2$GDpct = exp(census2$logit_gd) / (1 + exp(census2$logit_gd))
```

## BCG construction Step 2: Calculate GoDutch number of cycle commuters for each OD pair.
```{r}
# Calculate future cycle commuter no. based on Go Dutch scenario.
census2 =
  census2%>%
  mutate(bicycle_gd = all*GDpct)

# Check
census2 %>%
  mutate(check = bicycle_gd > bicycle) %>%
  group_by(check) %>%
  summarise(n())
#FALSE	22467	OD pairs have already achieved Dutch propensity.		
#TRUE	359983	

census2 %>%
  filter(bicycle > bicycle_gd) %>%
  arrange(desc(bicycle)) %>%
  nrow() #22467

nrow(census2) #382450

22467/382450 #0.05874493

census2 %>%
  mutate(OverDutch = ifelse(bicycle > bicycle_gd,TRUE, FALSE)) %>%
  group_by(OverDutch)%>%
  summarise(bicycle = sum(bicycle), bicycle_gd = sum(bicycle_gd))

41567- 21290 #20277

# Actual future share is assumed to be unchanged for OD pairs which already achieved the Dutch propensity.
census2$bicycle_future =
  ifelse(census2$bicycle_gd > census2$bicycle,
         census2$bicycle_gd,
         census2$bicycle)

# Rearrange columns
names(census2)

census2 = 
  census2[,c("omsoa","dmsoa","all","bicycle","bicycle_future","bicycle_gd","GDpct","logit_gd","rf_dist_km","rf_avslope_perc","intra")]
```

## BCG construction Step 3: Aggregate by destination MSOA.
```{r}
# Aggregate based on destination MSOA.
census3 =
  census2 %>%
  select(c(1:7))%>%
  group_by(dmsoa)%>%
  summarise(all = sum(all),
            bicycle = sum(bicycle),
            bicycle_future = sum(bicycle_future),
            bicycle_gd = sum(bicycle_gd))

# How many MSOAs in GL?
length(unique(census2$dmsoa)) #983

# Check
sum(census2$all) == sum(census3$all) # TRUE
sum(census2$bicycle) == sum(census3$bicycle) # TRUE
sum(census2$bicycle_future) == sum(census3$bicycle_future) # TRUE
sum(census2$bicycle_gd) == sum(census3$bicycle_gd) # TRUE
```

## BCG construction Step 4: Construct BCG by mean values
```{r}
# Calculate current share for each MSOA
census3$CurrentShare = census3$bicycle/census3$all

# Calculate future share for each LSOA.
census3$FutureShare = census3$bicycle_future/census3$all

# Calculate growth share and add a new column.
census3$Growth = census3$FutureShare - census3$CurrentShare

# Horizontal axis (Current AT share)
# If the share is lower than the mean, 1 otherwise 2.

BCG_x = ifelse(
  census3$CurrentShare < mean(census3$CurrentShare),
  1,2)

# Vertical axis (Growth AT share)
# If the share is lower than the mean, 1 otherwise 2.

BCG_y = ifelse(
  census3$Growth < mean(census3$Growth),
  1,2)

# Combine the above two.
BCG = paste(BCG_x,BCG_y,sep="")

# Rename the codes to BCG terms.
BCG = recode(BCG, 
              '11' = "Problematic", 
              '12' = "Questionable",
              '21' = "Achieved",
              '22' = "Promising")

# Add a column.
census3$BCG = BCG

census3$BCG = factor(census3$BCG, 
                levels = c("Promising","Achieved","Questionable","Problematic"))

# Current, Future Share and growth max.
max(census3$CurrentShare) #0.148398
max(census3$FutureShare) #0.3400569
max(census3$Growth) #0.3242483
```

## Parking 1: Aggregate parking space for each MSOA
```{r}
# the updated parking data
parking
sum(parking$space) #140788

# Aggregate parking capacity based on MSOA
parking2 =
  parking %>%
  select(msoa, space) %>%
  group_by(msoa) %>%
  summarise(space = sum(space))

sum(parking2$space) == sum(parking$space) #140788 TRUE
```

## Parking 2: Join parking space to census
```{r}
census3 = left_join(census3, parking2, by = c("dmsoa" = "msoa"))
sum(census3$space) == sum(parking2$space) #TRUE Successful!
```

# Parking Occupancy Rate: por

4 Categories:
Surplus  : Less than 50% occupancy rate
Ideal    : 50% and more and 80% and less occupancy rate
Threshold: More than 80% and 100% and less occupancy rate
Shortage : More than 100% occupancy rate

Examples:
Surplus  : bicycle= 30, parking=100 - Less than 50% occupancy rate
Ideal    : bicycle= 70, parking=100 - 50% and more and 80% and less occupancy rate
Threshold: bicycle= 90, parking=100 - More than 80% and 100% and less occupancy rate
Shortage : bicycle=110, parking=100 - More than 100% occupancy rate

Exceptions:
Case 1   : bicycle= 0, parking=100 -> Surplus  (n = 22 current)
Case 2   : bicycle=10, parking=0   -> Shortage (n = 1  current)
Case 3   : bicycle= 0, parking=0   -> Shortage (n = 0  observation)

## Current Occupancy Rate and Category
```{r}
# Current Occupancy Rate
census3$porCurrent = census3$bicycle / census3$space

census3%>%
  filter(bicycle == 0)
census3%>%
  filter(space == 0)

# Categorise into 4.
## 2011 Occupancy Rate
census3 = 
  census3 %>%
    mutate(porCurrentCat = ifelse(porCurrent > 1, "Shortage", 
                          ifelse(0.8 < porCurrent & porCurrent <= 1, "Threshold",
                                 ifelse(0.5 <= porCurrent & porCurrent <= 0.8, "Ideal",
                                        ifelse(0.5 > porCurrent, "Surplus",NA))))
           )
census3
```

## Future Occupancy Rate and Category
```{r}
# Future Occupancy Rate
census3$porFuture = census3$bicycle_future / census3$space

# Categorise into 4.
## 2011 Occupancy Rate
census3 = 
  census3 %>%
    mutate(porFutureCat = ifelse(porFuture > 1, "Shortage", 
                          ifelse(0.8 < porFuture & porFuture <= 1, "Threshold",
                                 ifelse(0.5 <= porFuture & porFuture <= 0.8, "Ideal",
                                        ifelse(0.5 > porFuture, "Surplus",NA))))
           )

census3
```

## por checking
```{r}
### Check data
census3 %>%
  group_by(porCurrentCat)%>%
  summarise(n())

census3 %>%
  group_by(porFutureCat)%>%
  summarise(n())

nrow(census3) #983

census3 %>%
  group_by(porCurrentCat)%>%
  summarise(n = n())%>%
  select(n)%>%
  sum() #983

census3 %>%
  group_by(porFutureCat)%>%
  summarise(n = n())%>%
  select(n)%>%
  sum() #983
```

## Reorder factor of por categorisation
```{r}
# Convert to factor.
census3$porCurrentCat = as.factor(census3$porCurrentCat)
census3$porFutureCat  = as.factor(census3$porFutureCat)

# Check levels
levels(census3$porCurrentCat)
levels(census3$porFutureCat)
#"Ideal"     "Shortage"  "Surplus"   "Threshold"

# Reorder factor levels
census3$porCurrentCat = factor(census3$porCurrentCat, 
                levels = c("Surplus","Ideal","Threshold","Shortage"))
census3$porFutureCat = factor(census3$porFutureCat, 
                levels = c("Surplus","Ideal","Threshold","Shortage"))


# Check levels
levels(census3$porCurrentCat)
levels(census3$porFutureCat)
#"Surplus"   "Ideal"     "Threshold" "Shortage" 
```

# Figures
### Figure 9 Histogram of Current and Future Share of Cycle Commuter
```{r}
current = data.frame(share = census3$CurrentShare)
future  = data.frame(share = census3$FutureShare)

current$category = 'Current'
future$category  = 'Future'

shareCF <- rbind(current, future)

ggplot(shareCF, aes(share, fill = category)) + geom_density(alpha = 0.2)

ggplot(shareCF, aes(share, fill = category)) + 
  geom_histogram(alpha = 0.2, position = "identity", binwidth = 0.01) +
  labs(y="Frequency", x = "Current and Future Share of Cycle Commuter")
```

### Figure 14 Histogram of Growth Share of Cycle Commuter
```{r}
# Mean, Median, Max., Min.
mean(census3$Growth) #0.1950014
median(census3$Growth) #0.1923137
max(census3$Growth) #0.3242483
min(census3$Growth) #0.06974227

# Histogram
ggplot(census3, aes(x = Growth)) +
  geom_histogram(position = "identity", 
                 binwidth = 0.01,
                 fill = "grey", 
                 color = "black"
                 )+
  labs(y="Frequency", x = "Growth Share of Cycle Commuter")
```

### Figure 16 Scatter Plot of Growth and Current Share of Cycle Commuter
```{r}
BCGcol = c("#368cd3", "#73d87d", "#ffff01", "#ff3b40")

ggplot(census3, aes(x = CurrentShare, y = Growth)) +
  geom_point(aes(color = BCG), size = 1) +
  scale_colour_manual(values=BCGcol) + 
  geom_line(aes(x = mean(CurrentShare))) +
  geom_line(aes(y = mean(Growth))) +
  labs(y="Current Share", x = "Growth Share") +
  labs(colour = "PCTxBCG Category")+
  labs(y="Growth Share of Cycle Commuter", x = "Current Share of Cycle Commuter")

mean(census3$CurrentShare)*100 #3.563695
mean(census3$Growth)*100 #19.50014
```

### Figure 17 Violin Plot of Growth and Current Share of Cycle Commuter
```{r}
# Mutate and label data based on current share, categorise into 5.
vplot= census3 %>%
  mutate(vplot = ifelse(CurrentShare < 0.03, "0-3%",
                        ifelse(0.03 <= CurrentShare & CurrentShare < 0.06, "3-6%", 
                               ifelse(0.06 <= CurrentShare & CurrentShare < 0.09, "6-9%",
                                      ifelse(0.09 <= CurrentShare & CurrentShare < 0.12, "9-12%",
                                             ifelse(0.12 <= CurrentShare, "12-15%" , NA)))))
         )%>%
  select(CurrentShare, Growth,vplot) 

# Convert to factor.
vplot$vplot = as.factor(vplot$vplot)

# Reorder factor.
vplot$vplot = factor(vplot$vplot,
                     levels = c("0-3%","3-6%","6-9%","9-12%","12-15%"))

ggplot(vplot, aes(x=vplot, y=Growth,  color =vplot)) + 
  geom_violin() + 
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y="Growth Share of Cycle Commuter", x = "Current Share of Cycle Commuter")

ggplot(vplot, aes(x=vplot, y=Growth,  color =vplot)) + 
  geom_violin() + 
  geom_boxplot(width=0.1)+
  labs(y="Growth Share of Cycle Commuter", x = "Current Share of Cycle Commuter")


vplot %>%
  group_by(vplot)%>%
  summarise(n= n(), min = min(Growth), max = max(Growth)) %>%
  mutate(range = max -min)
```

### Figure 20 Histogram of Parking Space per MSOA
```{r}
# Total capacity of parking in Greater London.
sum(census3$space) #140788

# Mean, Median, Max., Min.
mean(census3$space) #143.2228
median(census3$space) #76
max(census3$space) #3010
min(census3$space) #0
sd(census3$space) #222.0242
skewness(census3$space) #5.320692

# High concentration of parking space on the small numbers of MSOA?
census3 %>%
  arrange(desc(space)) %>%
  select(space)%>%
    top_n(-983*0.3)%>%
  sum() #16609

16609/140788  #10  - 12%
62544/140788  #100 - 44%
61303/140788  #10% - 44%
95165/140788  #25% - 68%
123889/140788 #50% - 88%

6160/140788   #-30% - 4%

# Histogram
ggplot(census3, aes(x = space)) +
  geom_histogram(position = "identity", 
                 binwidth = 10,
                 fill = "grey", 
                 color = "black"
                 )+
  labs(y="Frequency", x = "Parking Capacity per MSOA")
```

### Figure 21 Breakdown of Parking Space by No. of Cycle Commuter (left) and Area (right)
```{r}
# Join area to census 3.
census3 = left_join(census3, area, by = c("dmsoa" = "msoa"))
```

```{r}
# Categorise into 6 ranges.
tbd= 
  census3 %>%
  mutate(space2 = ifelse(space == 0, "None", 
                          ifelse(1 <= space & space <= 100, "1-100",
                                 ifelse(100 < space & space <= 300, "100-300",
                                        ifelse(300 < space & space <= 500, "300-500",
                                               ifelse(500 < space & space <= 1000, "500-1000",
                                                      ifelse(1000 < space,"1000-",NA))))))
           )

tbd2= tbd %>%
  group_by(space2)%>%
  summarise(all = sum(all), bicycle = sum(bicycle),area = sum(area_sqm))

tbd2$space2 = as.factor(tbd2$space2)
levels(tbd2$space2)
tbd2$space2 = factor(tbd2$space2, 
                levels = c("None","1-100","100-300","300-500","500-1000","1000-"))

tbd2$area_kmsq = tbd2$area/1000^2
tbd2$area_kmsq = as.numeric(tbd2$area_kmsq)

# Size in terms of area
(1002575971+ 65723076 )/ 1573508480  #0.6789281 by small numbers

31713098 / 1573508480 #0.02015439

# Size in terms of cyclist
(511+ 21666 )/ 143182  #0.1548868 by small numbers
sum(tbd2$bicycle)
45138 / 143182 #0.3152491

  

ggplot(tbd2,aes(x=space2, y = all)) +
  geom_bar( stat="identity")+
  labs(y="No. of Commuter by All Modes", x = "Parking Space")

ggplot(tbd2,aes(x=space2, y = bicycle)) +
  geom_bar( stat="identity")+
  labs(y="No. of Commuter by Bicycle", x = "Parking Space")

ggplot(tbd2,aes(x=space2, y = area_kmsq)) +
  geom_bar( stat="identity")+
  labs(y="Area (sq.km)", x = "Parking Space")
```

### Figure 24 Histogram of Current Parking Demand per MSOA (>500 excluded)
```{r}
# Total capacity of parking in Greater London.
sum(census3$bicycle) #143182

# Mean, Median, Max., Min.
mean(census3$bicycle) #145.6582
median(census3$bicycle) #42
max(census3$bicycle) #13053
min(census3$bicycle) #0
skewness(census3$bicycle) #13.97264

# Histogram
ggplot(census3, aes(x = bicycle)) +
  geom_histogram(position = "identity", 
                 binwidth = 50,
                 fill = "grey", 
                 color = "black"
                 )+
  labs(y="Frequency", x = "Current Parking Demand per MSOA")

census3 %>%
  filter(bicycle > 0, bicycle < 500) %>%
    ggplot(aes(x = bicycle)) +
  geom_histogram(position = "identity", 
                 binwidth = 10,
                 fill = "grey", 
                 color = "black"
                 )+
  labs(y="Frequency", x = "Current Parking Demand per MSOA")
```

### Figure 27 Histogram of Future Parking Demand per MSOA (>1,000 excluded)
```{r}
sum(census3$bicycle_future) #613945.6

sum(census3$bicycle_future)/ sum(census3$bicycle) #4.287868 times more than current demand.


# Mean, Median, Max., Min.
mean(census3$bicycle_future) #624.5631
median(census3$bicycle_future) #336.1253
max(census3$bicycle_future) #35034.31
min(census3$bicycle_future) #34.61217
sd(census3$bicycle_future) #1561.68
skewness(census3$bicycle_future) #14.13697

# Histogram
ggplot(census3, aes(x = bicycle_future)) +
  geom_histogram(position = "identity", 
                 binwidth = 50,
                 fill = "grey", 
                 color = "black"
                 )+
  labs(y="Frequency", x = "Future Parking Demand per MSOA")

census3 %>%
  filter(bicycle_future > 0, bicycle_future < 1000) %>%
    ggplot(aes(x = bicycle_future)) +
  geom_histogram(position = "identity", 
                 binwidth = 10,
                 fill = "grey", 
                 color = "black"
                 )+
  labs(y="Frequency", x = "Future Parking Demand per MSOA")
```

### Figure 31 Breakdown of Parking Occupancy Category based on No. of Cyclist for Current Scenario (left) and Future Scenario (right)
### Figure 32 Percentage Breakdown of Parking Occupancy Category based on No. of Cyclist for Current Scenario (left) and Future Scenario (right)
```{r}
tbd =
  census3 %>%
  group_by(BCG, porCurrentCat) %>%
    summarise(count = n(), cyclists = sum(bicycle))

col_pocu = c("#368cd3", "#73d87d", "#ffff01" ,"#ff3b40")

# Charts by No of MSOA
# Stacked barchart
ggplot(tbd, aes(fill=porCurrentCat, y=count, x=BCG))  + 
    geom_bar(position="stack", stat="identity")+
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of MSOA", x = "BCG Category")

# Percent stacked barchart
ggplot(tbd, aes(fill=porCurrentCat, y=count, x=BCG))  + 
    geom_bar(position="fill",  stat="identity", ) +
  scale_fill_manual(values=col_pocu)

# Charts by No of MSOA
# Stacked barchart
ggplot(tbd, aes(fill=porCurrentCat, y=cyclists, x=BCG))  + 
    geom_bar(position="stack", stat="identity")+
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of Cyclist", x = "PCTxBCG Category")

# Percent stacked barchart
ggplot(tbd, aes(fill=porCurrentCat, y=cyclists, x=BCG))  + 
    geom_bar(position="fill",  stat="identity", ) +
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of Cyclist", x = "PCTxBCG Category")
```

```{r}
# Group by BCG and parking availability category based on GoDutch
tbd =
  census3 %>%
  group_by(BCG, porFutureCat) %>%
    summarise(count = n(), cyclists = sum(bicycle_future))


# Charts by No of LSOA
# Stacked barchart
ggplot(tbd, aes(fill=porFutureCat, y=count, x=BCG))  + 
    geom_bar(position="stack", stat="identity")+
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of MSOA", x = "BCG Category")

# Percent stacked barchart
ggplot(tbd, aes(fill=porFutureCat, y=count, x=BCG))  + 
    geom_bar(position="fill",  stat="identity", ) +
  scale_fill_manual(values=col_pocu)

# Charts by No of Cyclists
# Stacked barchart
ggplot(tbd, aes(fill=porFutureCat, y=cyclists, x=BCG))  + 
    geom_bar(position="stack", stat="identity")+
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of Cyclist", x = "PCTxBCG Category")

# Percent stacked barchart
ggplot(tbd, aes(fill=porFutureCat, y=cyclists, x=BCG))  + 
    geom_bar(position="fill",  stat="identity", ) +
  scale_fill_manual(values=col_pocu)+
  labs(fill = "Parking\n Occupancy")+
  labs(y="No. of Cyclist", x = "PCTxBCG Category")

col_pocu = c("#368cd3", "#73d87d", "#ffff01" ,"#ff3b40")
```

### Figure 33 Scatter Plot of Parking Space and No. of Cyclist by MSOA for Current Scenario 
```{r}
ggplot(census3, 
       aes(x = bicycle, 
           y = space,
           color = BCG)
       )+
  geom_point(size = 1) +
  scale_colour_manual(values=BCGcol) +
  geom_abline(intercept = 0, 
              slope = 1, 
              color="red", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:1
  geom_abline(intercept = 0, 
              slope = 1.25, 
              color="black", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:1.2
  geom_abline(intercept = 0, 
              slope = 2, 
              color="blue", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:2
  xlim(0,NA)+
  ylim(0,NA)+
  facet_wrap( ~ BCG, ncol=4)+
  labs(y="Parking Capacity", x = "Current No. of Cycle Commuter")
```

```{r}
ggplot(census3, 
       aes(x = bicycle, 
           y = space,
           color = BCG)
       )+
  geom_point(size = 1) +
  scale_colour_manual(values=BCGcol) +
  geom_abline(intercept = 0, 
              slope = 1, 
              color="red", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:1
  geom_abline(intercept = 0, 
              slope = 1.25, 
              color="black", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:1.2
  geom_abline(intercept = 0, 
              slope = 2, 
              color="blue", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:2
  xlim(0,1000)+
  ylim(0,500)+
  facet_wrap( ~ BCG, ncol=4)+
  labs(y="Parking Capacity", x = "Current No. of Cycle Commuter")
```

### Figure 34 Scatter Plot of Parking Space and No. of Cyclist by MSOA for Future Scenario
```{r}
# GoDutch - Plot provision of parking per BCG.
ggplot(census3, 
       aes(x = bicycle_future, 
           y = space,
           color = BCG)
       )+
  geom_point(size = 1) +
  scale_colour_manual(values=BCGcol) +
  geom_abline(intercept = 0, 
              slope = 1, 
              color="red", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:1
  geom_abline(intercept = 0, 
              slope = 1.25, 
              color="black", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:1.2
  geom_abline(intercept = 0, 
              slope = 2, 
              color="blue", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:2
  xlim(0,NA)+
  ylim(0,NA)+
  facet_wrap( ~ BCG, ncol=4)+
  labs(y="Parking Capacity", x = "Future No. of Cycle Commuter")
```

```{r}
# GoDutch - Plot provision of parking per BCG.
ggplot(census3, 
       aes(x = bicycle_future, 
           y = space,
           color = BCG)
       )+
  geom_point(size = 1) +
  scale_colour_manual(values=BCGcol) +
  geom_abline(intercept = 0, 
              slope = 1, 
              color="red", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:1
  geom_abline(intercept = 0, 
              slope = 1.25, 
              color="black", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:1.2
  geom_abline(intercept = 0, 
              slope = 2, 
              color="blue", 
              linetype="dashed", 
              size=0.5) + # Cyclist:Parking=1:2
  xlim(0,1000)+
  ylim(0,500)+
  facet_wrap( ~ BCG, ncol=4)+
  labs(y="Parking Capacity", x = "Future No. of Cycle Commuter")
```